\chapter{Acknowledgements}
\label{chpr:acknowledgement}

I would first like to thank my thesis advisor Prof. Marazzina for the always prompt help in writing the research.
Then I would like to thank Prof. Ametrano, who initially unveiled me the true nature of Bitcoin as a tool enhancing freedom, successively assisted me in my learning growth, ultimately he directed me in my research, advicing me when facing doubts and putting me back on track when I needed. 

Next I would like to acknowledge the experts whose work is the skeleton of the thesis, Peter Todd and Andrew Poelstra.
Todd is the first contributor to OpenTimestamps, his code and publications have been the essential landmark which inspired almost the whole research.
Poelstra is the author of the code extension that enables the technique examined in the research.

Furthermore I would like to thank the community behind Milano Bitcoin meetups, they give me the chance to meet experts and enthusiastic people, it motivated me to deepen my studies and contributed to improve my education in the subject.

Finally, I would like to profoundly thank the Eternity Wall team, specially Riccardo Casatta, Valerio Vaccaro and Luca Vaccaro.
Eternity Wall, leading company in the sector, hosted me for an internship during which the research was written, 
their mentorship has been indispensable to achieve the results composing this work.
They patiently counseled me in each step I had to take, teaching me the correct approach to tackle and solve specific technical problems in a professional manner. 
With extreme and consistent availability, they deeply involved me in the subject, sparking in me profound motivations.